---
title: "ML Transformation Estimates - ROC"
author: "Michael Harrison"
date: "May 4, 2017"
output: html_document
---

#Load Libraries
```{r, warning=FALSE}
library(caret)
library(pROC)
library(lubridate)
library(ROSE)
#For parallel processing
library(parallel)
library(doParallel)
```

# Training Initialization 
- Training Harness
```{r}
fitControl <- trainControl(method = "repeatedcv", number = 10, repeats = 3,
                           classProbs = TRUE, summaryFunction = twoClassSummary)
metric <- "ROC"
seed <- 10
training$CARAVAN <- make.names(training$CARAVAN, unique = FALSE)
```

#Configure parallel Processing
```{r}
#Configures parallel processing
paraOn <- function(){
        cluster <- makeCluster(detectCores()-1)
        registerDoParallel(cluster)}

paraOff <- function(){
        cluster <- makeCluster(detectCores()-1)
        stopCluster(cluster)
        registerDoSEQ()}

para <- function(state){
        cluster <- makeCluster(detectCores()-1)
        if(state == "on"){
                start.time <- Sys.time()
                registerDoParallel(cluster)
        }
        if(state == "off"){
                stopCluster(cluster)
                registerDoSEQ()
                end.time <- Sys.time()
                elapsed = end.time - start.time
                return(elapsed)
        }
        else{
                stop()
        }
}
```

#Baseline Algorithm Suite

##GLMNET
```{r}
paraOn()
set.seed(seed)
fitGLMNET.trans <- train(CARAVAN~., data = training, 
             method = "glmnet", metric = metric,
             preProc = c("BoxCox"),
             trControl = fitControl)
paraOff()
fitGLMNET.trans
```

##Random Forest
```{r}
start.time <- Sys.time()
paraOn()
set.seed(seed)
fitRF.trans <- train(CARAVAN~., data = training,
                method = "rf", metric = metric,
                preProc = c("BoxCox"),
                trControl = fitControl)
end.time <- Sys.time()
time.takenRF.trans <- end.time - start.time
paraOff()
fitRF.trans
```


#Support Vector Machines
```{r}
#Support Vector Machines w/ Radial Basis Function
paraOn()
set.seed(seed)
fitSVM.trans <- train(CARAVAN~., data = training, 
             method = "svmRadial", metric = metric,
             preProc = c("BoxCox"),
             trControl = fitControl)
paraOff()
fitSVM.trans
```


##K Nearest Neighbors
```{r}
paraOn()
set.seed(seed)
fitKNN.trans <- train(CARAVAN~., data = training, 
             method = "knn", metric = metric,
             preProc = c("BoxCox"),
             trControl = fitControl)
paraOff()
fitKNN.trans
```


##Stochastic Gradient Boosting
```{r}
paraOn()
set.seed(seed)
fitGBM.trans <- train(CARAVAN~., data = training,
                method = "gbm", metric = metric,
                preProc = c("BoxCox"),
                trControl = fitControl, verbose = FALSE)
paraOff()
fitGBM.trans
```
 
#Compare Results
```{r}
transformResults <- resamples(list(SVM = fitSVM.trans,
                                  GLMNET = fitGLMNET.trans,
                                  RF = fitRF.trans,
                                  KNN = fitKNN.trans,
                                  GBM = fitGBM.trans))
```

```{r}
scales <- list(x = list(relation = "free"),
               y = list(relation = "free"))
dotplot(transformResults, main = "Transformed Algorithm Suite Results", 
        scales = scales)
```

```{r}
summary(transformResults)
```

```{r}
transTiming <- seconds_to_period(transformResults$timings$Everything)
time.taken.trans <- list(overSVM = transTiming[1],
                   overGLMNET = transTiming[2],
                   overRF = transTiming[3],
                   overKNN = transTiming[4],
                   overGBM = transTiming[5])
time.taken.over
```

#Predict with Validation Set

##Prepare transform using training data
```{r}
set.seed(seed)
x <- training[,1:85]
preprocessParams <- preProcess(x, method = c("BoxCox"))

valX <- validation[,1:85]
trans_valX <- predict(preprocessParams, valX)
valY <- validation[,86]
valY<- make.names(valY, unique = FALSE)

```

##SVM Predictions

```{r}
pred_fitSVM.trans <- predict(fitSVM.trans, newdata=trans_valX, type="prob")
pred_fitSVM.roc <- roc(valY, pred_fitSVM.trans$X1)
pred_fitSVM.roc$auc
```

##GLMNET Predictions
```{r}
pred_fitGLMNET.trans <- predict(fitGLMNET.trans, newdata=trans_valX, type="prob")
pred_fitGLMNET.roc <- roc(valY, pred_fitGLMNET.trans$X1)
pred_fitGLMNET.roc$auc
```

##Random Forest Predictions
```{r}
pred_fitRF.trans <- predict(fitRF.trans, newdata=trans_valX, type="prob")
pred_fitRF.roc <- roc(valY, pred_fitRF.trans$X1)
pred_fitRF.roc$auc
```

##KNN Predictions
```{r}
pred_fitKNN.trans <- predict(fitKNN.trans, newdata=trans_valX, type="prob")
pred_fitKNN.roc <- roc(valY, pred_fitKNN.trans$X1)
pred_fitKNN.roc$auc
```

##GBM Predictions
```{r}
pred_fitGBM.trans <- predict(fitGBM.trans, newdata=trans_valX, type="prob")
pred_fitGBM.roc <- roc(valY, pred_fitGBM.trans$X1)
pred_fitGBM.roc$auc
```

```{r}
AUC_transformResults <- list(transformSVM = pred_fitSVM.roc$auc,
                        transformGLMNET = pred_fitGLMNET.roc$auc,
                        transformRF = pred_fitRF.roc$auc,
                        transformKNN = pred_fitKNN.roc$auc,
                        transformGBM = pred_fitGBM.roc$auc)
AUC_transformResults
```

